A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-11 6_validation.tex
overhaul of printing results section (reviewer 2.5)
describe DfAM implications (reviewer 1.1)

We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using $N=3$, all with a preferred bead widths of $w^* = \SI{0.4}{\milli\meter}$. The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

\subsection{Computational results}

@@

\subsection{Printing results}
\revise{
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs \emph{linear advance} for accurately realizing adaptive deposition width:
gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines narrower than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

The prints are shown in \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
The prints which employ the uniform offsets technique show a lot of underfill, which impacts the visual quality of the print.
Moreover, in the case of the regular honeycomb there are several fully disconnected hexagons, which means the object falls apart.
The difference between the centered and the inward distributed schemes is less pronounced.
We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extreme bead widths.
The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
}{
\input{6_2_printing_results}
}

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
\end{subfigure}
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
\caption{Centered}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
The uniform technique produces distinct underfill areas.
The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
The inward distributed scheme produces the least defects.
}
\label{prints}
\end{figure}

>>>>

\revise{}
{
\subsection{Theoretical considerations}
Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
For the center scheme and for the current state-of-the-art one should only avoid parts for which $(i + 0.8) w^* < d < (i+ 1.25) w^*$ in order to avoid underfill.
For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
where $w_\text{min}$ is a configarable parameter when using the widening meta-scheme.

\todo{limitations}
}

\revise{}
{
\subsection{Computational results}
}
We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using $N=3$, all with a preferred bead widths of $w^* = \SI{0.4}{\milli\meter}$. The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

@@

\revise{
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs \emph{linear advance} for accurately realizing adaptive deposition width:
gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines narrower than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

The prints are shown in \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
The prints which employ the uniform offsets technique show a lot of underfill, which impacts the visual quality of the print.
Moreover, in the case of the regular honeycomb there are several fully disconnected hexagons, which means the object falls apart.
The difference between the centered and the inward distributed schemes is less pronounced.
We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extreme bead widths.
The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
\end{subfigure}
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
\caption{Centered}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
The uniform technique produces distinct underfill areas.
The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
The inward distributed scheme produces the least defects.
}
\label{prints}
\end{figure}
}{}
